\section{2-prong Vtag Scale Factors}
As seen in our studies and presentations, we need calibation/scale factors for our 2-prong V-tagger. This methodology was taken from HIG-24-017 and we use code borrowed from them. The setup is a bit annoying, but it is as follows.

\subsection{Setup}
The first thing to do is get the proper setup described by A. Novak in the Github repository involving this code~\cite{2prong}. Note that it might be good to set up a new workspace for this as well. It can also fit into the \verb|Fit| workspace since it uses the same CMSSW version. This starts by making sure to implement \verb|rhalphalib|. The general steps are:

\begin{verbatim}
    cmsrel CMSSW_14_1_0_pre4
    cd CMSSW_14_1_0_pre4/src
    cmsenv
    scram-venv
    cmsenv
    git clone https://github.com/cms-analysis/HiggsAnalysis-CombinedLimit.git \
        HiggsAnalysis/CombinedLimit
    cd HiggsAnalysis/CombinedLimit
    git checkout v10.1.0
    scram b -j4
    python3 -m pip install git+https://github.com/nsmith-/rhalphalib.git
\end{verbatim}

\noindent There are tests given in the repository for \verb|rhalphalib|~\cite{rhalphalib} that you can run to make sure it installed properly. Once this is done, the code for the 2-prong tagger SF can be installed. So far, your working directory should look like this:

\begin{verbatim}
    [your_working_space]/CMSSW_14_1_0_pre4/src/HiggsAnalysis/CombinedLimit
\end{verbatim}

\noindent While inside this folder, do the following:

\begin{verbatim}
    git clone https://github.com/andrzejnovak/TnPSF.git
    cd TnPSF
\end{verbatim}

\noindent Then, you can run the commands given in the tagger library's README file~\cite{2prong}. You need to modify it to use the proper files you want. 

\subsection{Additional Useful Files}
At the current time where the \verb|ttbar_selection| branch has not been merged back into the main branch, the following macros only exist on this branch, so keep this in mind when looking for them. 

\subsubsection{plot\_WTag\_CR}
\verb|plot_WTag_CR.py| is a script created to plot the control region used for this 2-prong V-tag stuff. This produces the plots seen on Slide 15 of our May 7th presentation~\cite{vqqhcc_twiki}. Running the scripts above produces the plots shown on Slide 16.

\subsubsection{prepare\_templates}
\verb|prepare_templates.py| and \verb|prepare_templates_v2.py| (probably just need the second one) are scripts created to produce the necessary templates that are needed for the 2-prong tagger SF code. Rather than using the templates they give, replace them with ones generated by this script.